---
title: "Practical Machine Learning_Project"
author: "Field"
date: "2016年7月4日"
output: html_document
---

Here is the project for the Coursera courses Practical Machine Learning. We are using the data to predict how people's activity will be.

#Load the data 
First of all, we should load the data to see the structure. 
```{r}
setwd("/users/field/desktop/Practical Machine Learning")
raw_train <- read.csv("pml-training.csv",stringsAsFactors = FALSE,na.strings = c("NA",""))
raw_test <- read.csv("pml-testing.csv",stringsAsFactors = FALSE,na.strings = c("NA",""))
```

#Data cleaning
Then we may want to use columns with no NAs.
```{r}
NAs <- apply(raw_train,2,function(x) {sum(is.na(x))}) 
cleanTrain <- raw_train[,which(NAs == 0)]
cleanTest <- raw_test[,which(NAs == 0)]
```

So far we have datasets with no NAs, then we need to remove columns composed of strings.

```{r}
removeIndex <- as.integer(c(1,2,3,4,5,6))
trainSet <- cleanTrain[,-removeIndex]
testSet <- cleanTest[,-removeIndex]
```

Then we use 70% of the data as our cross validation set.
```{r}
library(lattice)
library(ggplot2)
library(caret)
trainIndex <- createDataPartition(y = trainSet$classe, p=0.7,list=FALSE)
trainSet <- trainSet[trainIndex,]
crossValidationSet <- trainSet[-trainIndex,]
```


#Model training
First of all, we can choose among these models. So let's start with random forest.
```{r}

control <- trainControl(method = "cv", number = 4)
modelFit <- train(trainSet$classe~., data = trainSet, method = "rf",trControl = control)
```

Then we may try some other algorithms like linear regression and glm.
But the models seem to have some errors. Thus we will use the random forest as our final model.

#Calculation the errors
We can use the cross validation set to measure the sample error.
```{r}
predicted <- predict(modelFit, crossValidationSet)
SampleError <- sum(predicted == crossValidationSet$classe)/nrow(crossValidationSet)
SampleError
```

#Generating data for the prediction vector
```{r}
answers <- predict(modelFit,testSet)
```
